Using HbA1c and Fasting BG to Predict Development of CFRD

### 2025-07-11 Christine Chan/CF Registry/cf_registry_CFRD_prediction.qmd
CFRD joint model predictions

```{r setup}
#| include: false
library(survival)
library(nlme)
library(JM)
library(dplyr)
library(tidyr)
library(arsenal)
library(knitr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

>>>>

```{r setup}
#| include: false
library(survival)
library(nlme)
library(JM)
library(dplyr)
library(tidyr)
library(arsenal)
library(knitr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
nd <- joint_fit_value$data
nd$pred <- predict(joint_fit_value, registry[registry$eDWID %in% reg_include, ], type = "Subject",idVar = "eDWID")
```
